### 2018-04-30 paper/message-passing-design.tex
lala
algo

\NewScheme{\SPOR}{SPOR}

@@

\NewAlgorithm{\Send}{Send}
\NewAlgorithm{\Fwd}{Forward}
\NewAlgorithm{\Recv}{Receive}
\NewVariable{\rdv}{rdv}

@@

In contrast to Tor~\cite{Tor} that provides only one address per hop
in the route, \name provides for each layer of the onion several
alternatives for the next hop in the route depending on their
probability of being online. To implement our  probabilistic
predictive onion routing mechanism, \name defined three different algorithms to
receive, send and forward messages among users' \squad. For instance,
if Alice wants to send a message \(m\) to Bob, Bob uses the
\(\SPOR[\Recv]\) algorithm (See \cref{SPORRecv}) to create a probabilistic onion route \(H_\rdv\) from
 a rendez-vous point to its own devices from its \squad --- all the hops on the route are 
chosen by Bob uniformly at random from the RPS. \(\SPOR[\Recv]\)
returns the \(H_\rdv\) that Bob gives to Alice using an
out-of-band channel, \eg using one device of its \squad.
PORs have \(L\) layers, and for each layer the number of
alternatives nodes depends of a failure threshold \(\theta\). 
As long as \(\theta\) is not exceeded, alternatives nodes are added in
\(H_\rdv\) as depicted in \cref{ExtendRoute}. Thus the probability of
failure for the extension is \(1 - (1 - \theta)^L\).

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
  \caption{\label{fig:file-exchange}%
    A schematic of Alice and Bob sending a message using \(\SPOR\).
  }
\end{figure}

\NewAlgorithm{\ExtendRoute}{ExtendRoute}
\NewAlgorithm{\CreateOnionLayer}{CreateOnionLayer}

\begin{figure}

  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    \Require{%
      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
      \(D\) is a set of device addresses.
      $\pk_D$ is the public key of device set $D$.
      $L$ is the length of the route,
      $\theta$ is the threshold of probability of failure.%
    }
    \Function{\ExtendRoute}{$H, L, \theta$}
      \If{$L\leq 0$}
        \State \Return $H$
      \EndIf
      \State $D\gets \CreateOnionLayer[\theta]$
      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
      \State \Return $\ExtendRoute[H, L-1, \theta]$
    \EndFunction
  \vspace{0.3em}
    \Function{\CreateOnionLayer}{$\theta$}
      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
      \State $D\gets \{(d, \pk_d, p_d)\}$
      \While{$\prod_{d\in D} p_d > \theta$}
        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
      \EndWhile
      \State \Return $D$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{ExtendRoute}%
    \scriptsize
    The \(\ExtendRoute\) algorithm extends a route \(H\)
  }
\end{figure}

\NewAlgorithm{\Store}{Store}
\NewAlgorithm{\Dec}{Dec}
\NewVariable{\sk}{sk}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}
    \Require{%
      $D$ is the set of alternative recipient devices.
    }
    \Function{\SPOR[\Recv]}{$D$}
      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
      \State \Return $H_\rdv$
        \Comment{Give to sender out-of-bound.}
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{SPORRecv}%
\scriptsize
    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
  }
\end{figure}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}
    \Require{%
      $m$ is the message to be sent,
      $H_\rdv$ is the onion-route given by the recipient.
    }
    \Function{\SPOR[\Send]}{$H_\rdv, m$}
      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
      \State $D\concat C_H\gets H_\rdv$
      \For{$d\in D$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H, m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{SPORSend}%
    \scriptsize
    The \(\SPOR[\Send]\) algorithm 
  }
\end{figure}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}
    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
    \Function{\SPOR[\Fwd]}{$C_H, m$}
      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
      \If{$H = \bot$}
        \State \Return $\bot$
      \EndIf
      \State $\{d_i\}\concat C_H'\gets H$
      \If{$C_H' = \top$}
        \State \Return $\Store[m]$
      \EndIf
      \For{$d\in \{d_i\}$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H', m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
    \Function{\Store}{$m$}
      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
      \If{$m = \bot$}
        \State \Return $\bot$
      \EndIf
      \State Store $m$ to disk.
      \State \Return $\top$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{SPORFwd}%
    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
    by decrypting \(C_H\) with the node's associated private key.
    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
    is intended for the local node and \(c_m\) is instead sent to disk using 
    \(\Store\) (\cref{SPORRecv}).%
  }
\end{figure}

>>>>

\NewScheme{\SPOR}{SPORES}

@@

\NewAlgorithm{\Fwd}{Forward}
\NewAlgorithm{\Send}{BuildRouteSender}
\NewAlgorithm{\Recv}{BuildRouteReceiver}
\NewAlgorithm{\ExtendRoute}{ExtendRoute}
\NewAlgorithm{\CreateOnionLayer}{CreateOnionLayer}
\NewAlgorithm{\Dec}{Dec}
\NewAlgorithm{\Store}{Store}
\NewVariable{\sk}{sk}
\NewVariable{\rdv}{rdv}
\NewVariable{\LRV}{\mathcal{L_{RV}}\xspace}
\NewVariable{\Hsend}{\mathcal{H}_{\text{send}}\begin{algorithmic}[1]}
\NewVariable{\Hrec}{\mathcal{H}_{\text{rec}}\begin{algorithmic}[1]}
\NewVariable{\Hforward}{\mathcal{H}_{\text{forward}}\begin{algorithmic}[1]}
\NewVariable{\Hbackward}{\mathcal{H}_{\text{backward}}\begin{algorithmic}[1]}
\NewVariable{\Hsendforward}{\mathcal{H}_{\text{send forward}}\begin{algorithmic}[1]}
\NewVariable{\Hsendbackward}{\mathcal{H}_{\text{send backward}}\begin{algorithmic}[1]}
\NewVariable{\Hrecforward}{\mathcal{H}_{\text{rec forward}}\begin{algorithmic}[1]}
\NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec backward}}\begin{algorithmic}[1]}

@@

The principle of onion routing à la Tor~\cite{Tor} is to put nodes relaying messages between a source and a destination.
By employing encryption layers, a relay doesn't know where it is situated on the message's path. 
It only knows who gave him the message, and where to send it to.

In contrast to Tor~\cite{Tor} that provides only one address per hop
in the route, \name provides, for each layer of the onion, several
alternative nodes for the next hop in the route depending on their
probability of being online. 
We call our modified onion routes Probabilistic Onion Routes or PORs.

Another difference from Tor, where connections are established by all nodes in the route, \name is stateless: the route's ends (the sender Alice and receiver Bob) cooperate to create the headers containing all the necessary routing information for future communication between Alice and Bob.
In that regard, two headers are required: $\Hforward$ to route packets from Alice to Bob, and $\Hbackward$ for packets from Bob to Alice.

To implement our predictive onion routing mechanism, \name is thus split in two algorithms: the route building one, and the message routing one.
Figure~\ref{fig:file-exchange} shows the process of the route creation until the first exchange of a file chunk from Alice to Bob.
Bob uses the backward route to send acknowledgments back to Alice.

\begin{figure}[t]
  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
  \caption{\label{fig:file-exchange}A schematic of the creation and usage of PORs between Alice and Bob's e-squads.}
\end{figure}

\subsubsection{Building routes} 
\label{ssub:building_routes}

When Alice wants to send a file to Bob, they first have to call the route building algorithm, and to exchange relevant information out of band (e.g. using mail, or their phones' bluetooth connection).
They create a route of $L$ layers, a configuration parameter that must be odd. We introduce $l=(L-1)/2$.
Bob (the receiver) initiates the route creation. 
He randomly chooses nodes to constitute a rendez-vous layer \LRV, and nodes to constitute $l$ layers from \LRV to his \squad. 
We come back on layer creation below.
He crafts a layered encrypted header (more details below) to \LRV (excluded) to his squad (included), that we will call \Hrecforward.
He also crafts his part of the header for the backward route, \Hrecbackward: it contains the route from Bob's \squad (excluded) to \LRV (included).

Bob sends \Hrecforward and the descriptors of the \LRV nodes to Alice.
Alice still has her part of the route to create: like Bob, she randomly picks nodes to constitutes $l$ layers from her \squad to \LRV.

\paragraph*{Layer creation}

\paragraph*{Header preparation}

\begin{figure}[t]
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    % \Require{%
    %   $D$ is the set of alternative recipient devices.
    % }
    \Function{\Recv}{$D$}
      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
      \State \Return $H_\rdv$
        \Comment{Give to sender out-of-bound.}
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}

  \vspace{0.3em}
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    % \Require{%
    %   $m$ is the message to be sent,
    %   $H_\rdv$ is the onion-route given by the recipient.
    % }
    \Function{\Send}{$H_\rdv, m$}
      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
      \State $D\concat C_H\gets H_\rdv$
      \For{$d\in D$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H, m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}

  \vspace{0.3em}
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    % \Require{%
    %   $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
    %   \(D\) is a set of device addresses.
    %   $\pk_D$ is the public key of device set $D$.
    %   $L$ is the length of the route,
    %   $\theta$ is the threshold of probability of failure.%
    % }
    \Function{\ExtendRoute}{$H, L, \theta$}
      \If{$L\leq 0$}
        \State \Return $H$
      \EndIf
      \State $D\gets \CreateOnionLayer[\theta]$
      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
      \State \Return $\ExtendRoute[H, L-1, \theta]$
    \EndFunction
  \vspace{0.3em}
    \Function{\CreateOnionLayer}{$\theta$}
      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
      \State $D\gets \{(d, \pk_d, p_d)\}$
      \While{$\prod_{d\in D} p_d > \theta$}
        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
      \EndWhile
      \State \Return $D$
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}
  \caption{\label{fig:route building algo}The route building algorithm}
\end{figure}

\subsubsection{Routing messages}
\label{ssub:routing_messages}

\begin{figure}[t]
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    %\Require{$\pk, \sk$ is the public--private key-pair of the node.}
    \Function{\SPOR[\Fwd]}{$C_H, m$}
      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
      \If{$H = \bot$}
        \State \Return $\bot$
      \EndIf
      \State $\{d_i\}\concat C_H'\gets H$
      \If{$C_H' = \top$}
        \State \Return $\Store[m]$
      \EndIf
      \For{$d\in \{d_i\}$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H', m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}

  \begin{algorithmic}[1]
    \Function{\Store}{$m$}
      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
      \If{$m = \bot$}
        \State \Return $\bot$
      \EndIf
      \State Store $m$ to disk.
      \State \Return $\top$
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}
  \caption{\label{SPORFwd}%
    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
    by decrypting \(C_H\) with the node's associated private key.
    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
    is intended for the local node and \(c_m\) is instead sent to disk using 
    \(\Store\) (\cref{SPORRecv}).%
  }
\end{figure}

For instance, if Alice wants to send a message \(m\) to Bob, they are both going to perform a part of the building algorithm.
Bob uses the \(\SPOR[\Recv]\) function (See \cref{SPORRecv}) to create a probabilistic onion route $\mathcal{H_B}$ from
 a rendez-vous (RV) layer $\mathcal{L_{RV}}$ to its own devices from its \squad---all the hops on the route are 
chosen by Bob uniformly at random from the Global Overlay.
 \(\SPOR[\Recv]\)
returns $\mathcal{H_B}$ and  that Bob gives to Alice using an
out-of-band channel, \eg using one device of its \squad.
PORs have \(L\) layers, and for each layer the number of
alternatives nodes depends of a failure threshold \(\theta\). 
As long as \(\theta\) is not exceeded, alternatives nodes are added in
\(H_\rdv\) as depicted in \cref{ExtendRoute}. Thus the probability of
failure for the extension is \(1 - (1 - \theta)^L\).

@@
